DATA 621 - Business Analytics and Data Mining

### 2020-10-27 HW3/HW3_Final_AA.Rmd
add model 2, remove stacked

## Model 2
<!-- ### Stacked Classifier -->

<!-- ```{r m2setup} -->
<!-- cv_folds <- vfold_cv(train_df, v = 10, repeats = 1) -->

<!-- crime_recipe <- recipe(target ~., data=train_df) -->

<!-- crime_wf<- workflow() %>% -->
<!--   add_recipe(crime_recipe) -->

<!-- crtl_grid <- control_stack_grid() -->
<!-- ``` -->

<!-- Specify the models. Using SVM as another model to blend with the logistic.  -->

<!-- ```{r m2svm} -->
<!-- logit_specs <-  -->
<!--   logistic_reg( -->
<!--     penalty = tune(), -->
<!--     mixture = tune() -->
<!--     ) %>% -->
<!--   set_engine("glm") %>% -->
<!--   set_mode("classification") -->

<!-- svm_specs <-  -->
<!--   svm_rbf( -->
<!--     cost = tune(), -->
<!--     rbf_sigma = tune(), -->
<!--     margin = tune() -->
<!--   ) %>% -->
<!--   set_mode("classification") %>% -->
<!--   set_engine("kernlab") -->
<!-- ``` -->

<!-- Tuning the models for best parameters. The stack function will cherry pick the -->
<!-- models that best optimize the blended final model.  -->

<!-- ```{r m2stack} -->
<!-- svm_wf <- -->
<!--   crime_wf %>% -->
<!--   add_model(svm_specs) -->

<!-- svm_results<- -->
<!--   tune_grid( -->
<!--     svm_wf,  -->
<!--     resample = cv_folds, -->
<!--     control = crtl_grid, -->
<!--     grid = 10, -->
<!--     save_pred = TRUE, -->
<!--     save_workflow = FALSE -->
<!--   ) -->

<!-- logit_wf <-  -->
<!--   crime_wf %>% -->
<!--   add_model(logit_specs) -->

<!-- logit_results <- -->
<!--   tune_grid( -->
<!--     logit_wf, -->
<!--     resamples = cv_folds, -->
<!--     control = crtl_grid, -->
<!--     grid = 10, -->
<!--     save_pred = TRUE, -->
<!--     save_workflow = FALSE -->
<!-- ) -->
<!-- ``` -->

<!-- Blend! -->

<!-- ```{r m2Blend} -->
<!-- crime_model_stack <- -->
<!--   stacks() %>% -->
<!--   add_candidates(logit_results) %>% -->
<!--   add_candidates(svm_results) %>% -->
<!--   blend_predictions() %>% -->
<!--   fit_members() -->

<!-- crime_model_stack -->
<!-- ``` -->

<!-- ```{r m2Predict} -->
<!-- crime_pred <- -->
<!--   test_df %>% -->
<!--   bind_cols(predict(crime_model_stack, ., type = "prob"), -->
<!--             predict(crime_model_stack, ., type = "class")) -->
<!-- ``` -->

<!-- Computing the metrics for the stacked model: -->

<!-- ```{r m2Stats} -->
<!-- roc<- yardstick::roc_auc( -->
<!--   crime_pred, -->
<!--   truth = target, -->
<!--   contains(".pred_1") -->
<!--   ) -->

<!-- acc<- yardstick::accuracy( -->
<!--   crime_pred, -->
<!--   truth = target, -->
<!--   estimate = .pred_class -->
<!-- ) -->

<!-- recall<- yardstick::recall( -->
<!--   crime_pred, -->
<!--   truth = target, -->
<!--   estimate = .pred_class -->
<!-- ) -->

<!-- precise<- yardstick::precision( -->
<!--   crime_pred, -->
<!--   truth = target, -->
<!--   estimate = .pred_class -->
<!-- ) -->
<!-- metrics_df<- -->
<!--   bind_rows(roc, acc, recall, precise) -->

<!-- crime_pred %>% -->
<!--   conf_mat(truth = target, estimate = .pred_class) -->

<!-- metrics_df -->
<!-- ``` -->

@@

<!-- The blended model is comprised of two sub-models, the logistic and the SVM. -->
<!-- Below are the prediction results for each sub-model.  -->

<!-- ```{r} -->
<!--  best_model_metric <- select_best(svm_results, "accuracy") -->
<!--  finalize_workflow(svm_wf, best_model_metric) %>% -->
<!--    last_fit(data_split) %>% -->
<!--    collect_metrics() -->

<!--  logit_wf %>% -->
<!--    last_fit(data_split) %>% -->
<!--    collect_metrics() -->

<!--  logit_wf %>% -->
<!--    fit(data = train_df) %>% -->
<!--    pull_workflow_fit() %>% -->
<!--    vip(geom = "col", aesthetics = list(fill='red4')) -->
<!-- ``` -->

<!-- We see that they are both in the low eighties percent for accuracy, and low -->
<!-- nineties for roc auc. Together make for a better overall prediction.  -->

<!-- We again see that the primary predictor in the logistic regression is the `nox` -->
<!-- with `rad` and `ptratio` rounding out the top three predictors. This is in line -->
<!-- with the base model. Living close to the center of town, having teachers, and -->
<!-- not having polluted air are the largest predictors in terms of above median crime.  -->

>>>>

## Model 2
### Logistic Classifier

```{r m2setup}
cv_folds <- vfold_cv(train_df, v = 10, repeats = 1)

crime_recipe <- recipe(target ~., data=train_df)

crime_wf<- workflow() %>%
  add_recipe(crime_recipe)
```

```{r m2svm}
logit_specs <-
  logistic_reg(
    penalty = tune(),
    mixture = tune()
    ) %>%
  set_engine("glm") %>%
  set_mode("classification")

Tuning the models for best parameters.

```{r m2stack}
logit_wf <-
  crime_wf %>%
  add_model(logit_specs)

logit_results <-
  tune_grid(
    logit_wf,
    resamples = cv_folds,
    control = crtl_grid,
    grid = 10,
    save_pred = TRUE,
    save_workflow = FALSE
)
```

```{r m2predict}
best_model_auc <- select_best(logit_results, "roc_auc")
final_auc<-
  finalize_workflow(
    logit_wf,
    best_model_auc
)

final_model_pred<-
  final_auc %>%
  last_fit(data_split) %>%
  collect_predictions()

Computing the metrics for the logit model:

```{r m2Stats}
roc<- yardstick::roc_auc(
  final_model_pred,
  truth = target,
  contains(".pred_1")
  )

acc<- yardstick::accuracy(
  final_model_pred, 
  truth = target, 
  estimate = .pred_class
)

recall<- yardstick::recall(
  final_model_pred,
  truth = target,
  estimate = .pred_class
)

precise<- yardstick::precision(
  final_model_pred,
  truth = target,
  estimate = .pred_class
)
metrics_df<-
  bind_rows(roc, acc, recall, precise)

crime_pred %>%
  conf_mat(truth = target, estimate = .pred_class)
```

@@

Below the feature importances for the logistic model.

```{r}
logit_wf %>%
  last_fit(data_split) %>%
  collect_metrics()

logit_wf %>%
  fit(data = train_df) %>%
  pull_workflow_fit() %>%
  vip(geom = "col", aesthetics = list(fill='red4'))
```

We again see that the primary predictor in the logistic regression is the `nox`
with `rad` and `ptratio` rounding out the top three predictors. This is in line
with the base model. Living close to the center of town, having teachers, and
not having polluted air are the largest predictors in terms of above median crime.
